% !Mode:: "TeX:UTF-8"

\chapter{Citations}
\section{Getting current \LaTeX{} document to use your .bib file}
At the end of your \LaTeX~file (that is, after the content, but before \lstinline[language={[LaTeX]TeX}]|\end{document}|), you need to place the following commands:

\begin{lstlisting}[language={[LaTeX]TeX}]
\bibliographystyle{plain}
\bibliography{sample1,sample2,...samplen}
% Note the lack of whitespace between the commas and the next bib file.
\end{lstlisting}

Bibliography styles are files recognized by BibTeX that tell it how to format the imformation stored in the .bib file when processed for output. And so the first command listed above is declaring which style file to use. The style file in this instance is plain.bst (which comes as standard with BibTeX). You do not need to add the .bst extension when using this command, as it is assumed. Despite its name, the plain style does a pretty good job (look at the output of this tutorial to see what I mean).

The second command is the one that actually specifies the .bib file you wish to use. The ones I created for this tutorial were called sample1.bib, sample2.bib,..., samplen.bib, but once again, you don't include the file extension. At the moment, the .bib file is in the same directory as the \LaTeX~document too. However, if your .bib file was elsewhere (which makes sense if you intend to maintain a centralized database of references for all your research), you need to specify the path as well, e.g.

\lstinline[language={[LaTeX]TeX}]|\bibliography{/some/where/sample}| or \lstinline[language={[LaTeX]TeX}]|\bibliography{../sample1}| (if the .bib file is in the parent directory of the .tex document that calls it).

Now that \LaTeX~and BibTeX know where to look for the appropriate files, actually citing the references is fairly trivial. The \lstinline[language={[LaTeX]TeX}]|\cite{ref_key}| is the command you need, making sure the \textit{ref\_key} corresponds exactly to one of the entries in the .bib file. If you wish to cite more than one reference at the same time, do the following: \lstinline[language={[LaTeX]TeX}]|\cite{ref_key1, ref_key2, ..., ref_keyN}|

\section{Bibtex bibliography styles}
The next two commands are the ones that set the bibliography style and import the bibliography file. See \textcolor{red}{Bibliography management with bibtex} for more information.

\begin{lstlisting}[language={[LaTeX]TeX}]
\bibliographystyle{stylename}
\bibliography{bibfile}
\end{lstlisting}

where \textit{bibfile} is the name of the \textit{bibliography.bib} file without extension and \textit{stylename} is one of the following:

\begin{itemize}
\item \textcolor{red}{abbrv}\\
Items are cited: \textit{The \LaTeX~Companion} book [2], the Einstein journal paper [1], and The \LaTeX~related items are [2,3].

\textbf{References} 

[1] A. Einstein. Zur Elektrodynamik bewegter K\"{o}rper. (German) [On the electrodynamics of moving bodies]. \textit{Annalen der Physik}, 322(10):891-921, 1905.

[2] M. Goossens, F. Mittelbach, and A. Samarin. \textit{The \LaTeX~Companion}. Addison-Wesley, Reading, Massachusetts, 1993.

[3] D. Knuth. Knuth: Computers and typesetting.

\item \textcolor{red}{acm}\\
Items are cited: \textit{The \LaTeX~Companion} book [2], the Einstein journal paper [1], and The \LaTeX~related items are [2,3].

\textbf{References}

[1] EINSTEIN, A. Zur Elektrodynamik bewegter K\"{o}rper. (German) [On the electrodynamics of moving bodies]. \textit{Annalen der Physik, 322}, 10 (1905), 891-921.

[2] GOOSSENS, M., MITTELBACH, F., AND Samarin, A. \textit{The \LaTeX~Companion}. Addison-Wesley, Reading, Massachusetts, 1993.

[3] KNUTH, D. Knuth: Computers and typesetting.

\item \textcolor{red}{alpha} \\
Items are cited: \textit{The \LaTeX~Companion} book [GMS93], the Einstein journal paper [Ein05], and The \LaTeX~related items are [GMS93,Knu]

\textbf{References}

[Ein05]~~~Albert Einstein. Zur Elektrodynamik bewegter K\"{o}rper. (German) [On the electrodynamics of moving bodies]. \textit{Annalen der Physik}, 322(10):891-921, 1905.

[GMS93] Michel Goossens, Frank Mittelbach, and Alexander Samarin. \textit{The \LaTeX~Companion}. Addison-Wesley, Reading, Massachusetts, 1993.

[Knu]~~~~Donald Knuth. Knuth: Computers and typesetting.

\item \textcolor{red}{apalike}\\
Items are cited: \textit{The \LaTeX~Companion} book [Goossens et al., 1993], the Einstein journal paper [Einstein, 1905], and The \LaTeX~related items are [Goossens et al., 1993,Knuth,].

\textbf{References}

[Einstein, 1905] Einstein, A.(1905). Zur Elektrodynamik bewegter K\"{o}rper. (German) [On the electrodynamics of moving bodies]. \textit{Annalen der Physik}, 322(10):891-921.

[Goossens et al., 1993] Goossens, M., Mittelbach, F., and Samarin A. (1993). \textit{The \LaTeX~Companion}. Addison-Wesley, Reading, Massachusetts.

[Knuth,] Knuth, D. Knuth: Computers and typesetting.

\item \textcolor{red}{ieeetr}\\
Items are cited: \textit{The \LaTeX~Companion} book [1], the Einstein journal paper [2], and The \LaTeX~related items are [1,3].

\textbf{References} 

[1] M. Goossens, F. Mittelbach, and A. Samarin. \textit{The \LaTeX~Companion}. Reading, Massachusetts: Addison-Wesley, 1993.

[2] A. Einstein. "Zur Elektrodynamik bewegter K\"{o}rper. (German) [On the electrodynamics of moving bodies]," \textit{Annalen der Physik}, vol. 322, no. 10, pp. 891-921, 1905.

[3] D. Knuth. "Knuth: Computers and typesetting."

\item \textcolor{red}{plain}\\
Items are cited: \textit{The \LaTeX~Companion} book [1], the Einstein journal paper [2], and The \LaTeX~related items are [1,3].

\textbf{References} 

[1]  Albert Einstein. Zur Elektrodynamik bewegter K\"{o}rper. (German) [On the electrodynamics of moving bodies]. \textit{Annalen der Physik}, 322(10):891-921, 1905.

[2] Michel Goossens, Frank Mittelbach, and Alexander Samarin. \textit{The \LaTeX~Companion}. Addison-Wesley, Reading, Massachusetts, 1993.

[3] Donald Knuth. Knuth: Computers and typesetting.
\item \textcolor{red}{siam}\\
Items are cited: \textit{The \LaTeX~Companion} book [2], the Einstein journal paper [1], and The \LaTeX~related items are [2,3].

\textbf{References} 

[1] A. EINSTEIN, \textit{Zur Elektrodynamik bewegter K\"{o}rper. (German) [On the electrodynamics of moving bodies]}, Annalen der Physik, 322(1905), pp. 891-921.

[2] M. GOOSSENS, F. MITTELBACH, and A. SAMARIN. \textit{The \LaTeX~Companion}. Addison-Wesley, Reading, Massachusetts, 1993.

[3] D. KNUTH. \textit{Knuth: Computers and typesetting}.

\item \textcolor{red}{unsrt} \\
Items are cited: \textit{The \LaTeX~Companion} book [1], the Einstein journal paper [2], and The \LaTeX~related items are [1,3].

\textbf{References}

[1] Michel Goossens, Frank Mittelbach, and Alexander Samarin. \textit{The \LaTeX~Companion}. Addison-Wesley, Reading, Massachusetts, 1993.

[2] Albert Einstein. Zur Elektrodynamik bewegter K\"{o}rper. (German) [On the electrodynamics of moving bodies]. \textit{Annalen der Physik}, 322(10):891-921, 1905.

[3] Donald Knuth. Knuth: Computers and typesetting.
\end{itemize}
